Algorithm for Calculating Lightning Node Fees

### 2022-05-14 paper.tex
remove entanglement

  %   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %   %% Abstract                                 %%
  %   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{abstract}

  \end{abstract}

@@

The overall approach of this method is to set up a fee structure using the equivalent of the Helmholtz potential.
We will look at cases where a node operator may choose to entangle some channels based on a desire to ensure certain channels have a higher entropy than others based on transaction traffic.

@@

\section{Entanglement}
A node operator may wish to preferentially encourage or penalize a particular node to which they have a channel.
We can do this by looking expanding our single channel ensemble to that of the composite of the node.
This is done through the node's combined Hamiltonian.

If we take small routing node with three channels, there are $2^3$ possible routing combinations.
What the node operator can do is to entangle a pair of routing combinations by adjusting the corresponding off diagonal component of the Hamiltonian.
This will change the overall fee structure for the channel by correspondingly increasing or decreasing the ppm routing fee.

>>>>

  %   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  %   %% Abstract                                 %%
  %   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{abstract}
    This paper outlines a simple strategy to create channels on a Lightning Network routing node that will tend toward a balanced configuration.
    The algorithm is derived from the principles of statistical mechanics and uses the Helmholtz potential to dynamically assess either inbound or outbound fees.
  \end{abstract}

@@

The overall approach of this method is to set up a fee structure using the equivalent of the Helmholtz potential.

@@
